Generating Simulated Data

### 2021-04-29 docs/SimData.Rmd
length files in Gavin's format

>>>>

Reran the lendat code block above to make the survey-specific length input files with the new equal sized bins.

Now write input files in Gavin's format to have surveys together in one file:

```{r altinput, eval=FALSE}

allsvlenbin <- tibble()

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(survey, year, species, type, inpN, everything())

  allsvlenbin <- bind_rows(allsvlenbin, svlenbin)
}
write_csv(allsvlenbin, paste0(o.name,"observation_lengths_NOBA_allsurvs.csv"))
